Learning constraints in tabular data

### 2016-05-12 Paper/ECAI/tabular.tex
Updated table

\subsection{Error detection}
We consider two cases of error detection.
The first setting is the \textit{online} detection of errors which is similar to the autocompletion setting.
However, instead of considering viable constraints, we look at \textit{conflict} constraints, i.e. constraints that were learned at time~$t_0$ but do not agree with the newly added data at time~$t_1$.
Such conflict constraints can indicate errors in the input.
Since conflict constraints could also be accidental constraints that are correctly invalidated by the new data, the size of the data at timet~$t_0$ should be large enough.

The second type of error detection is \textit{offline} and attempts to detect errors in a spreadsheet.
Consider, for example, a use case concerning crime statistics provided by the FBI.
An extract of the spreadsheet is depicted in Figure~\ref{fig:fbi}.
When run on this sheet, our system is able to detect the second sum constraint, however, a missing value prevents the first sum constraint from being learned.
A possible approach to detect such missing or wrong values is to look at a sample of the table that excludes the erroneous row and compare the constraints learned on this sample with the constraints learned by adding the row containing the mistake.
The sample needs to large enough such that we have enough confidence that the constraints are correct.
If we define the sample to be our data at time~$t_0$ and the added row to be the additional input at~$t_1$, this task can be formulated as online error detection and dealt with in the same way.
Of course, generating large enough samples and rows (columns) to be added can be done in multiple ways.
In the limited case of detecting single errors one can leave out every row (column), consider the remaining data to be the sample and
and the left out row (column) to be new input.
\samuel{Should this be more specific?}

Error detection could be integrated more closely with the algorithm, reducing the computational complexity by looking for errors during the constraint learning phase.
This would, however, make the modeling constraints (considerably) more difficult.

\samuel{FBI: work out error detection algorithm}

(\sergey{I think there should be three things: key example evaluated, benchmark of 30 spreadsheets and maybe the FBI example, how we can detect interesting dependencies and correct potential mistakes})

\samuel{discussion: what would be a language to extend the system, what would be the user interface? can it be used by community?  can it be complitely automated? interaction with user and highlighing?
}

{\bfseries
  Experimental questions
}

\begin{itemize}
  \item  How accurate are we? (Accuracy / recall)
  \item  How fast are we and which factors affect the runtime (how)?
  \item  How general is our approach, what limitations are there?
\end{itemize}

>>>>

\subsection{Error detection}
We consider two cases of error detection.
The first setting is the \textit{online} detection of errors which is similar to the autocompletion setting.
However, instead of considering viable constraints, we look at \textit{conflict} constraints, i.e. constraints that were learned at time~$t_0$ but do not agree with the newly added data at time~$t_1$.
Such conflict constraints can indicate errors in the input.
Since conflict constraints could also be accidental constraints that are correctly invalidated by the new data, the size of the data at time ~$t_0$ should be large enough.

The second type of error detection is \textit{offline} and attempts to detect errors in a spreadsheet.
Consider, for example, a use case concerning crime statistics provided by the FBI.
An extract of the spreadsheet is depicted in Figure~\ref{fig:fbi}.
When run on this sheet, our system is able to detect the second sum constraint, however, a missing value prevents the first sum constraint from being learned.
A possible approach to detect such missing or wrong values is to look at a sample of the table that excludes the erroneous row and compare the constraints learned on this sample with the constraints learned by adding the row containing the mistake.
The sample needs to large enough such that we have enough confidence that the constraints are correct. For example, in Figure \ref{fig:fbi} all but one row satisfy the constraint, which is a strong indication that there is a constraint violation.
If we define the sample to be our data at time~$t_0$ and the added row to be the additional input at~$t_1$, this task can be formulated as online error detection and dealt with in the same way.
%Of course, generating large enough samples and rows (columns) to be added can be done in multiple ways.
%In the limited case of detecting single errors one can leave out every row (column), consider the remaining data to be the sample and
%and the left out row (column) to be new input.
